Comparing variations in sediment transport capacity between subglacial and subaerial systems

### 2023-03-23 theory.tex
GRL template added

  Additional processes and erosional hiatuses may further complicate signals of sediment discharge from glaciers in response to climate, compared to subaerial systems \citep{jansson2005,ganti2016}. 
  For instance, sediment expelled from a glacier in a transport-limited regime reacts, in addition to water discharge, to sediment discharge capacity defined by the thickness of the ice, controlling the closure of the channel, and the surface slope of the glacier, controlling water velocity \citep[Section~\ref{sect:sub_mode}; ] []{rothlisberger1972,shreve1972,delaney2022,stevens2022}.
  Conversely, sediment transport in most subaerial systems increases with water discharge and bed slope, with the bed slope, probably being more stable over yearly to century-scale time periods \citep[Section~\ref{sect:fluv}; e.g.][]{muller1968,whipple1999,wong2006,wickert2019}.

@@

  \section{Conclusions}
  Contrary to subaerial channels that can alter their channel width and water velocity in response to changing water discharge,
   pressurized subglacial channels accommodate changing water discharge by altering water velocity and shear stress, upon which sediment transport depends.
  This occurs because the size of subglacial channels evolves slowly compared to variations in water discharge.

>>>>

  Additional processes and erosional hiatuses may further complicate signals of sediment discharge from glaciers in response to climate, compared to subaerial systems \citep{jansson2005,ganti2016}. 
  For instance, sediment transport capacity from a glacier reacts to the ice thickness, controlling the closure of the channel, and the surface slope of the glacier, controlling water velocity \citep[Section~\ref{sect:sub_mode}; ] []{rothlisberger1972,shreve1972,delaney2022,stevens2022}, in addition to water discharge.
  Conversely, sediment transport in most subaerial systems increases with water discharge and bed slope, with the bed slope, probably being more stable over yearly to century-scale time periods \citep[Section~\ref{sect:fluv}; e.g.][]{muller1968,whipple1999,wong2006,wickert2019}.

@@

  \section{Conclusions}

  Pressurized subglacial channels accommodate changing water discharge by altering water velocity and shear stress, upon which sediment transport depends.
  This occurs because the size of subglacial channels evolves slowly compared to variations in water discharge.
  Conversely, subaerial channels can alter their channel width and water velocity in response to changing water discharge.
